---
title: '**The Finnish Top 0.4 Percent**: An Exploration of Top Tax Shares in Finland from 2009 to 2013'
author: "Kyle Ott and Cornelius Schneider"
date: "14 November 2014"
output:
  pdf_document:
    fig_caption: yes
    number_sections: yes
    toc: yes
bibliography:
- main1.bib
- packages1.bib
---

```{r, include=FALSE}
pkgs <- c('httr', 'dplyr', 'XML', 'ggplot2', 'stringr', 'car', 'devtools', 'rsdmx', 'stargazer', 'knitr', 'CausalImpact', 'repmis')
repmis::LoadandCite(pkgs, file = 'packages1.bib')
```





\pagebreak


# Introduction

```{r, results='asis'}
knitr::kable(sum2_table, align ='c', digits = c(4,5,7,2,12,13,4,3))
```

This is our introduction, state research question and motivate it a bit

# Our Unique, Tidy, Open, Reproducible Dataset

Briefly describe how we acquired the data

# Descriptive Statistics of Our Data


# Inferential Statistics: First Model Attempts

# Conclusion: Further Analysis Needed

***

This project used @CiteRStudio to create this research proposal.

\pagebreak

# References




